SCP Briefing Plots - Combined Intervention

### 2024-08-02 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Adding fix for US_household_upscaling to select the correct people

```{r}
# SF12_change_income_quint(summary_group = 'whole_pop',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen)
```

>>>>

```{r}
SF12_change_income_quint(summary_group = 'whole_pop',
                                    scen.list = scen.list)
# SF12_change_income_quint2(summary_group = 'whole_pop',
#                                     scen = scen)
```
